Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-08-28 Scripts/Initial_Analysis.Rmd
Included buble plot

##### Fig.Percentage Change Map

@@

##### Fig. 2 and S1. (Netowrk)

@@

##### Fig. 3 Mapping the time of emergence

@@

# Per EEZs
Eez_d_hist <- Eme_Res %>% 
  group_by(eezid ,sau_fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
    ) %>% 
  gather("metric","value",mean_yr:n_taxa) %>% 
  filter(metric != "n_taxa") %>% 
  mutate(
    reverse = abs(value-2100)  + 2000
  )

@@

>>>>

##### Fig. Percentage Change Map

@@

##### Fig. 1 and S1. (Netowrk)

@@

##### Fig. 2 Mapping the time of emergence

@@

# Per EEZs
Eez_d_hist <- Eme_Res %>% 
  group_by(eezid ,sau_fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
    ) %>% 
  gather("metric","value",mean_yr:n_taxa) %>% 
  # filter(metric != "n_taxa") %>% 
  mutate(
    reverse = abs(value-2100)  + 2000
  )

@@

##### Fig. 3. Bubble plot

```{r, buble_plot, eval = F, echo = F}

Buble_data <- Eez_d_hist %>% 
  filter(metric == "mean_yr") %>% 
  group_by(sau_fishing_entity,tresh) %>% 
  summarise(mean_yr = mean(value)) %>% 
  left_join(Eme_value_data,
            by = c("sau_fishing_entity","tresh")) %>% 
  filter(tresh == tresh_list[i],
         variable == "value") %>% 
  mutate(sum_value_mi = sum_value/1000000) %>%   # Million usd
  left_join(Matching_names,
            by = c("sau_fishing_entity","fishing_entity_id")) %>% 
  distinct(sau_fishing_entity,.keep_all = TRUE) %>% 
  filter(!is.na(un_geo_region)) %>% 
  ungroup() %>% 
  mutate(
    sau_fishing_entity = ifelse(sum_value_mi >= 1000 & !sau_fishing_entity %in% c("Spain"), paste(sau_fishing_entity,"*",sep = ""),sau_fishing_entity)
  )

# Plot the bubbles!

ggplot(Buble_data) +
  geom_point(
    aes(
      x = mean_yr,
      y = sum_value_mi,
      size = n_taxa,
      colour = un_geo_region
    ),
    alpha = 0.7
  ) +
  # scale_size(range = c(.1, 10), name="Fishing revenue (USD)")  +
  geom_label_repel(data = subset(Buble_data, sum_value_mi >= 1000),
                   aes(
                     x = mean_yr,
                     y = sum_value_mi,
                     label = sau_fishing_entity
                   ),
                   arrow = arrow(length = unit(0.009, "npc"), 
                                 type = "closed",
                                 ends = "first"),
                   force = 2,
                   box.padding = 2,
                   fill = "NA"

  ) +
  # scale_fill_viridis(discrete = F)
  scale_color_viridis(name="Georaphic Region",
                      discrete = T) +
  scale_x_continuous("Average time of emergence",
                     breaks = seq(2000,2080,20)
  ) +
  scale_y_continuous("Fishing revenue (million)",
                     breaks = seq(1000,5000,1000),
                     labels = scales::dollar
  ) +
  scale_size("Number of\nemerging taxa") +
  ggsave("./Figures/bubble_plot.png",
         width = 8,
         height = 8,
         units = "in"
  )
